\textbf{Political Instability and Financial Markets}

### 2017-08-23 doc/paper.tex
Reviewed most recent Polity IV and Archigos data files. Added two new coups to Table 1. We should add these events (Egypt 2013 and Thailand 2014) to the coup analysis.

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of Coup d'Etat}
\label{tab:coup list}\\
\vspace{-5pt}\\
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\endfirsthead
\multicolumn{3}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\hline
\endhead
\hline 
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
06/08/1970 & Argentina & Autocracy to autocracy\\
03/22/1971 & Argentina & Autocracy to autocracy (democracy by 1973)\\
03/24/1976 & Argentina & Democracy to autocracy\\
10/06/1976 & Thailand & Anocracy to autocracy\\
10/20/1977 & Thailand & Autocracy to autocracy\\
12/12/1979 & South Korea & Autocracy to autocracy\\
02/23/1991 & Thailand & Anocracy to anocracy\\
04/05/1992 & Peru & Democracy to anocracy\\
10/12/1999 & Pakistan & Democracy to autocracy\\
10/04/2002 & Nepal & Democracy to autocracy\\
09/19/2006 & Thailand & Democracy to anocracy\\
01/11/2007 & Bangladesh & Democracy to autocracy\\
 & \begin{tabular}[x]{@{}c@{}}\\\end{tabular} & \\
04/11/2002 & Venezuela & Partial/failed anocracy to democracy\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize

@@

We further supplement the CSP data with leadership data from Archigos Version 2.9, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g. coups, revolts and assassinations).

@@

An important question is whether other popular uprisings have had similar adverse economic consequences. To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 2.9 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent. These events are listed in \autoref{tab:protest-list} in the appendix.

>>>>

\singlespacing
\footnotesize
\begin{center}
\begin{longtable}[!ht]{l@{\extracolsep{\fill}}lll}
\caption{List of Coup d'Etat}
\label{tab:coup list}\\
\vspace{-5pt}\\
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\endfirsthead
\multicolumn{3}{c}%
{\tablename\ \thetable\ -- \textit{Continued from previous page}} \\
\hline
\hline
\multicolumn{1}{c}{Coup Date}&\multicolumn{1}{c}{Country}&\multicolumn{1}{c}{Coup Outcome}\\\hline
\hline
\endhead
\hline 
\multicolumn{3}{r}{\textit{Continued on next page}} \\
\endfoot
\hline
\endlastfoot
06/08/1970 & Argentina & Autocracy to autocracy\\
03/22/1971 & Argentina & Autocracy to autocracy (democracy by 1973)\\
03/24/1976 & Argentina & Democracy to autocracy\\
10/06/1976 & Thailand & Anocracy to autocracy\\
10/20/1977 & Thailand & Autocracy to autocracy\\
12/12/1979 & South Korea & Autocracy to autocracy\\
02/23/1991 & Thailand & Anocracy to anocracy\\
04/05/1992 & Peru & Democracy to anocracy\\
10/12/1999 & Pakistan & Democracy to autocracy\\
10/04/2002 & Nepal & Democracy to autocracy\\
09/19/2006 & Thailand & Democracy to anocracy\\
01/11/2007 & Bangladesh & Democracy to autocracy\\
07/03/2013 & Egypt & Anocracy to anocracy\\
05/22/2014 & Thailand & Democracy to anocracy\\
 & \begin{tabular}[x]{@{}c@{}}\\\end{tabular} & \\
04/11/2002 & Venezuela & Partial/failed democracy to democracy\\
\hline
\hline
\end{longtable}
\end{center}
\doublespacing
\normalsize

@@

We further supplement the CSP data with leadership data from Archigos Version 4.1, which allows us to identify additional cases in which a ``leader lost power through irregular means.'' Irregular transfers of power are those in which leaders do not leave office ``in a manner prescribed by either explicit rules or established conventions.'' Nearly all removals by irregular means result from the threat or use of force (e.g. coups, revolts and assassinations).

@@

An important question is whether other popular uprisings have had similar adverse economic consequences. To examine this, we explore all resignations that were driven by significant public protests.\footnote{The set of resignations includes all those listed in either the Coup d'etat Events Handbook or the Archigos Version 4.1 data set with available financial data. In practice, this is the 2011 Egyptian Revolution and the list or resignations in \autoref{tab:AR-resignations}.} Public protests include popular demonstrations, riots, non-violent civil resistance and other forms of public discontent. These events are listed in \autoref{tab:protest-list} in the appendix.
